FinalManuscript_DISCS_UG

### 2018-06-26 parts/02_relatedliterature.tex

However, there exists \textit{fully homomorphic} cryptosystems, where instead of being limited to operations like addition or multiplication, it allows any arbitrary operations on the ciphertext. It is only in recent years that a fully homomorphic cryptosystem has been described. Gentry's cryptosystem, which uses lattice-based cryptography, allows arbitrary functions that are constructed from various addition and multiplication operations \cite{gentry_fully_2009}. Gentry's cryptosystem allows for the computation of arbitrary Boolean circuits on binary data. While improvements have been developed for Gentry's original scheme \cite{hutchison_fully_2010 ,sen_homomorphic_2013}, since the homomorphic property of these systems is applied on each bit of the plaintext/ciphertext elementary addition and multiplication operations on the plaintext are compuationally intensive \cite{sen_homomorphic_2013, shortell_secure_2016}.

>>>>

However, there exists \textit{fully homomorphic} cryptosystems, where instead of being limited to operations like addition or multiplication, it allows any arbitrary operations on the ciphertext. It is only in recent years that a fully homomorphic cryptosystem has been described. Gentry's cryptosystem, which uses lattice-based cryptography, allows arbitrary functions that are constructed from various addition and multiplication operations \cite{gentry_fully_2009}. Gentry's cryptosystem allows for the computation of arbitrary Boolean circuits on binary data. While improvements have been developed for Gentry's original scheme \cite{hutchison_fully_2010, sen_homomorphic_2013}, since the homomorphic property of these systems is applied on each bit of the plaintext/ciphertext elementary addition and multiplication operations on the plaintext are compuationally intensive \cite{sen_homomorphic_2013, shortell_secure_2016}.
